Lab2

### 2021-08-03 src/data/DataCleaning.Rmd

@@

```{r clean dp03 data, echo=FALSE}
# filters by date/state
econ <- dp03_econ %>%
  rename(fips = GEO_ID, unemp_rate = DP03_0009PE) %>%
  select(fips, unemp_rate) %>%
  mutate(
    fips = substring(fips, 10),
    unemp_rate = as.double(unemp_rate)
  )

# merge into main dataframe
d <- merge(x = econ, y = d, by = c("fips"))
```

>>>>

unemp_claims <- readxl::read_excel("./../../data/raw/weekly-claims-by-county-twc.xlsx")

@@

```{r clean dp03 data, echo=FALSE}
econ <- dp03_econ %>%
  rename(fips = GEO_ID, unemp_rate = DP03_0009PE) %>%
  select(fips, unemp_rate) %>%
  mutate(
    fips = substring(fips, 10),
    unemp_rate = as.double(unemp_rate)
  )

# merge into main dataframe
d <- merge(x = econ, y = d, by = c("fips"))
```
```{r clean twc unemployment data, echo=FALSE}

uclaims <- unemp_claims[-c(1,2),] %>%
  select(TEXAS,
         ...6,
         ...7,
         ...8,
         ...9
         ) %>% 
  rowwise() %>%
  mutate(
    ...6 = as.integer(...6),
    ...7 = as.integer(...7),
    ...8 = as.integer(...8),
    ...9 = as.integer(...9),
    total_claims = sum(c(...6, ...7, ...8, ...9))
  ) %>%
  rename(
    county = TEXAS
  ) %>% drop_na()

# merge into main dataframe
d <- merge(x = select(uclaims, c(county, total_claims)), y = d, by = c("county"))
```
